Guided Proofreading of Automatic Segmentations for Connectomics

### 2018-03-08 paper/conclusion.tex
Update acknowledgements.

\section{Conclusions}

@@

Manual proofreading of connectomics segmentations is necessary, but it is a time consuming and error-prone task. We attempt to minimize manual labor and reduce the human bottleneck. Our classifiers can detect errors and suggest potential corrections to automatically improve segmentations, but performance can increase with guided human attention. Our approach makes it easier for both novices and experts to proofread successfully, and is significantly better than the existing baseline at this task. This helps reduce the human time spent finding and correcting errors, and so makes it faster to generate new ground truth label data. We provide our framework and data as free and open research at (source/data URL omitted for review).%\url{http://rhoana.org/guidedproofreading/}.

@@

%\section*{Acknowledgements}
%We would like to thank Stephen Plaza for detailed explanations of focused proofreading and Toufiq Parag for the configuration of the NeuroProof classifier.

>>>>

\vspace{-2mm}
\section{Conclusions}

@@

Manual proofreading of connectomics segmentations is necessary, but it is a time consuming and error-prone task. We attempt to minimize manual labor and reduce the human bottleneck. Our classifiers can detect errors and suggest potential corrections to automatically improve segmentations, but performance can increase with guided human attention. Our approach makes it easier for both novices and experts to proofread successfully, and is significantly better than the existing baseline at this task. This helps reduce the human time spent finding and correcting errors, and so makes it faster to generate new ground truth label data. We provide our framework and data as free and open research\footnote{\scriptsize{\url{http://rhoana.org/guidedproofreading/}}}.

@@

\vspace{-1mm}
\section*{Acknowledgements}
%We would like to thank Stephen Plaza for detailed explanations of \emph{Focused proofreading} and Toufiq Parag for the configuration of the \emph{NeuroProof} classifier. This research was supported in part by NSF grants IIS-1447344 and IIS-1607800, and by the Intelligence Advanced Research Projects Activity (IARPA) via Department of Interior/Interior Business Center (DoI/IBC) contract number D16PC00002.
We would like to thank Stephen Plaza for detailed explanations of \emph{Focused proofreading} and Toufiq Parag for the configuration of the \emph{NeuroProof} classifier. This research was supported in part by NSF grants IIS-1447344 and IIS-1607800, and by IARPA contract D16PC00002.
